Optimal (Multiway) Spatial Joins

### 2024-05-19 msj.tex
yufei

@@

>>>>

\extraspacing {\bf Math Conventions.}

@@

Year 2022 witnessed two independent works \cite{ty22,???} that reduce the time complexity of the $k$-SJ problem to $O((n + \out) \cdot \polylog n)$. Interestingly, neither \cite{ty22} nor \cite{???} studied $k$-SJ explicitly. In \cite{ty22}, Tao and Yi studied multiple variants of interval intersection joins under updates. The variant most relevant to our context is the following. For each $i \in [k]$, let $\I_i$ be a set of (one-dimensional) intervals in $\real$.
